---
title: "Results"
author: "Lion Schulz"
output:
  html_document:
    df_print: paged
---

# Notebook purpose

This notebook contains the code for the appendix

```{r}
source("backend/global_all.R")
```

# Confidence plot

## Set-up

```{r}
resolution_plots <- 100 # resolution for confidence plot
YI_vector <- seq(-10,10,length.out = resolution_plots) # creating x-grid
```



## As a function of $\sigma_I$

```{r}
sI_vector <- seq(1,5,by = .1) # setting different rhos

df_cI_sI <- expand.grid.df(YI_vector,as.factor(sI_vector),
                                 col_names = c("YI","sI"))
df_cI_sI$ci <- NA
```

```{r}
tI_fix <- 2
rho_fix <- .5

# Go through all the different rhos and compute confidence vectors for each
for (sI_temp in sI_vector){

  ci_vector <- cI.2o(YI = YI_vector,
                      sI = sI_temp,
                      tI = tI_fix,
                      rho = rho_fix,
                      a = 1) 
  
  # adding it to the dataframe
  df_cI_sI[which(df_cI_sI$sI == sI_temp),]$ci <- ci_vector
}
```


```{r}
# We first pick a colourscheme
palette_many_sI <- sequential_hcl(length(sI_vector)*1.3, "SunsetDark", rev = T)
palette_many_sI <- palette_many_sI[(length(palette_many_sI)-length(sI_vector)):length(palette_many_sI)] # we need to subset it to get along

df_subset_sI <- df_cI_sI[df_cI_sI$sI == 2,] # used to highlight the same confidence in the the 


pl_cI_by_sI <- ggplot(df_cI_sI,aes(YI,ci, colour = sI)) + 
                      geom_vline(xintercept = 0) +                     
                      geom_line(size = lsize) +
                      scale_y_continuous(name = bquote(c[I]),
                                         limits = c(0,1),
                                         breaks = c(0,.5,1)) +
                      scale_x_continuous(name = bquote(Y[I])) +
                      scale_color_manual(values = palette_many_sI) +
                      guides(colour = "none") +
                      geom_line(data = df_subset_sI,
                                aes(YI,ci),
                                colour = "grey", size = lsize)

pl_cI_by_sI
```

## As a function of $\tau_I$


```{r}
tI_vector <- seq(1,5,by = .1) # setting different rhos

df_cI_tI <- expand.grid.df(YI_vector,as.factor(tI_vector),
                                 col_names = c("YI","tI"))
df_cI_tI$ci <- NA
```

```{r}
sI_fix <- 2
rho_fix <- .5

# Go through all the different rhos and compute confidence vectors for each
for (tI_temp in tI_vector){

  ci_vector <- cI.2o(YI = YI_vector,
                      sI = sI_fix,
                      tI = tI_temp,
                      rho = rho_fix,
                      a = 1) 
  
  # adding it to the dataframe
  df_cI_tI[which(df_cI_tI$tI == tI_temp),]$ci <- ci_vector
}
```


```{r}
# We first pick a colourscheme
palette_many_tI <- sequential_hcl(length(tI_vector)*1.3, "Blues 3", rev = T)
palette_many_tI <- palette_many_tI[(length(palette_many_tI)-length(tI_vector)):length(palette_many_tI)] # we need to subset it to get along


pl_cI_by_tI <- ggplot(df_cI_tI,aes(YI,ci, colour = tI)) + 
                      geom_vline(xintercept = 0) +                     
                      geom_line(size = lsize) +
                      scale_y_continuous(name = bquote(c[I]),
                                         limits = c(0,1),
                                         breaks = c(0,.5,1)) +
                      scale_x_continuous(name = bquote(Y[I])) +
                      scale_color_manual(values = palette_many_tI) +
                      guides(colour = "none") +        
                      geom_line(data = df_subset_sI,
                                aes(YI,ci),
                                colour = "grey", 
                                size = lsize) +
  theme(axis.title.y = element_blank())
pl_cI_by_tI
```


## As a function of $rho_I$

```{r}
rho_vector <- seq(0.00,.95, by = .03) # setting different rhos

df_cI_by_rho <- expand.grid.df(YI_vector,as.factor(rho_vector),
                                 col_names = c("YI","rho"))
df_cI_by_rho$ci <- NA
```


```{r}
sI_fix <- 1.5
tI_fix <- 2

# Go through all the different rhos and compute confidence vectors for each
for (rho_temp in rho_vector){
  
  ci_vector <- cI.2o(YI = YI_vector,
                      sI = sI_fix,
                      tI = tI_fix,
                      rho = rho_temp,
                      a = 1) 
  
  # adding it to the dataframe
  df_cI_by_rho[which(df_cI_by_rho$rho == rho_temp),]$ci <- ci_vector
}
```


```{r}
pl_cI_by_rho <- ggplot(df_cI_by_rho,aes(YI,ci, colour = rho)) + 
                      geom_vline(xintercept = 0) +                    
                      geom_line(size = lsize) +
                      scale_y_continuous(name = bquote(c[I]),
                                         limits = c(0,1),
                                         breaks = c(0,.5,1)) +
                      scale_x_continuous(name = bquote(Y[I])) +
                      scale_color_viridis_d(direction = -1) +
                      guides(colour = "none") +
theme(axis.title.y = element_blank())
pl_cI_by_rho
```



## Posterior slopes


```{r}
# This function defines the slope when P(1|X,Y) = P(-1|X,Y)
posteriorequality <- function(sI,tI,rho){
  
  num <- sI^(-2) - rho/(sI*tI)
  num
  denom <- tI^(-2) - rho/(sI*tI)
  denom
  
  slope <- -num/denom
  return(slope)
}
```


### By $\sIgma_I$


```{r}
df_posterior_line_sI <- expand.grid.df(YI_vector,as.factor(sI_vector),
                                 col_names = c("XI","sI"))
df_posterior_line_sI$YI <- NA

for (sI_temp in sI_vector){
  
  slope_temp <-  posteriorequality(sI_temp,
                                   tI_fix,
                                   rho_fix)
  
  # forcing the vertical slope
  if (slope_temp %in% c(-Inf,Inf)) {
    slope_temp <- 10e3
  }
  
  
  # adding it to the dataframe
  df_posterior_line_sI[which(df_posterior_line_sI$sI == sI_temp),]$YI <- 
    df_posterior_line_sI[which(df_posterior_line_sI$sI == sI_temp),]$XI*slope_temp
}
```



```{r}
pl_posterior_line_by_sI <- ggplot(df_posterior_line_sI,aes(XI,YI, colour = sI)) + 
                            geom_line(size = lsize) +
                            scale_y_continuous(name = bquote(Y[I])) +
                            scale_x_continuous(name = bquote(X[I])) +
                            scale_color_manual(values = palette_many_sI) +
                            coord_cartesian(xlim = c(-10,10),
                                            ylim = c(-10,10)) + 
  guides(colour = "none")
pl_posterior_line_by_sI
```


## By $\tau_I$

```{r}
df_posterior_line_tI <- expand.grid.df(YI_vector,as.factor(tI_vector),
                                 col_names = c("XI","tI"))
df_posterior_line_tI$YI <- NA

for (tI_temp in tI_vector){
  
  slope_temp <-  posteriorequality(sI_fix,
                                   tI_temp,
                                   rho_fix)
  
    # forccing the vertical slope
  if (slope_temp %in% c(-Inf,Inf)) {
    slope_temp <- 10e3
  }
  
  # adding it to the dataframe
  df_posterior_line_tI[which(df_posterior_line_tI$tI == tI_temp),]$YI <- 
    df_posterior_line_tI[which(df_posterior_line_tI$tI == tI_temp),]$XI*slope_temp
}
```


And do the plotting

```{r}
pl_posterior_line_by_tI <- ggplot(df_posterior_line_tI,aes(XI,YI, colour = tI)) + 
                            geom_line(size = lsize) +
                            scale_y_continuous(name = bquote(Y[I])) +
                            scale_x_continuous(name = bquote(X[I])) +
                            scale_color_manual(values = palette_many_tI) +
                            coord_cartesian(xlim = c(-10,10),
                                            ylim = c(-10,10)) + 
                           guides(colour = "none") +
  theme(axis.title.y = element_blank())
pl_posterior_line_by_tI
```


### By $\rho_I$



```{r}
df_posterior_line_rho <- expand.grid.df(YI_vector,as.factor(rho_vector),
                                 col_names = c("XI","rho"))
df_posterior_line_rho$YI <- NA

for (rho_temp in rho_vector){
  
  slope_temp <-  posteriorequality(sI_fix,
                                   tI_fix,
                                   rho_temp)
  
  if (slope_temp %in% c(-Inf,Inf)) {
    slope_temp <- -1000
  }
  
  # adding it to the dataframe
  df_posterior_line_rho[which(df_posterior_line_rho$rho == rho_temp),]$YI <- 
    df_posterior_line_rho[which(df_posterior_line_rho$rho == rho_temp),]$XI*slope_temp
}
```


And do the plotting

```{r}
pl_posterior_line_by_rho <- ggplot(df_posterior_line_rho,aes(XI,YI, colour = rho)) + 
                            geom_line(size = lsize) +
                            scale_y_continuous(name = bquote(Y[I])) +
                            scale_x_continuous(name = bquote(X[I])) +
                            scale_color_viridis_d(direction = -1) +
                            coord_cartesian(xlim = c(-10,10),
                                            ylim = c(-10,10)) +   guides(colour = "none") +
theme(axis.title.y = element_blank())
pl_posterior_line_by_rho
```

## First plot together

```{r, fig.width=17, fig.height = 10.5}
pl_app_confidence <- pl_cI_by_sI + pl_cI_by_tI + pl_cI_by_rho + 
  pl_posterior_line_by_sI + pl_posterior_line_by_tI + pl_posterior_line_by_rho 
  plot_layout(guides = "collect")
  
pl_app_confidence
```


```{r}
ggsave(file = "output/MetaSearch_app_confidence.pdf",
       plot = pl_app_confidence,
       device = cairo_pdf,
       width = 17,
       height = 10.5,
       units = "in",
       dpi = 300)
```


# Cue-combination for the final confidence

First, we build a function that gets us the joint standard deviation

```{r}
zetaI.2o <- function(sI,tI,rho){
  zetaI <- cue_combination.2o(sI,tI,rho)$zetaI
}
```


## Varying $\tau_I$ and $\rho_I$

Plotting zeta for a fixed value of tau_I and varying sigma_I - first get the data

```{r}
# we define a range of sigma_I and a tau_I for this plot
sI_vector_zetaI <- seq(.75,5,.01)
tI_vector_zetaI <- c(1,2,4)
rho_vector_zetaI <- seq(0,1, by = .10)[1:10]

df_zetaI_vis <- expand.grid.df(sI_vector_zetaI,
                               tI_vector_zetaI,
                               rho_vector_zetaI,
                               col_names = c("sI","ti", "rho"))

df_zetaI_vis$zetaI <- zetaI.2o(df_zetaI_vis$sI,
                                df_zetaI_vis$ti,
                                df_zetaI_vis$rho)

df_zetaI_vis$rho <- as.factor(df_zetaI_vis$rho)
df_zetaI_vis$ti <- as.factor(df_zetaI_vis$ti)
```

```{r}
# function that translates standard deviation into accuracy
phi <- function(sd){
  pnorm(0,-1,sd)
}

df_zetaI_vis$phi_sI <-  phi(df_zetaI_vis$sI)
df_zetaI_vis$phi_zetaI <-  phi(df_zetaI_vis$zetaI)
```

```{r, fig.width=11, fig.height = 5}
axis_name_phi_zeta <- bquote(phi *"("*zeta["I"]*")")

pl_2o_zetaI_by_rho_phi <- ggplot(df_zetaI_vis,aes(phi_sI,phi_zetaI, colour = rho)) + 
                        geom_line(size = lsize) +
                        scale_y_continuous(name = axis_name_phi_zeta) +
                        scale_x_continuous(name = axis_name_initial_acc) +
                        scale_color_viridis_d(direction = -1) +
                        facet_wrap(.~ti,strip.position = "top")
pl_2o_zetaI_by_rho_phi
```


## As a function of $\tau_I$ and $\rho_I$ 

```{r}
# we define a range of sigma_I and a tau_I for this plot
tI_zetaI_vis <- seq(1,5,by = .5)

rhos_for_tI_zetaI_vis <- c(.2,.5,.8)

df_zetaI_vis_by_tI <- expand.grid.df(sI_vector_zetaI,
                               tI_zetaI_vis,
                               rhos_for_tI_zetaI_vis,
                               col_names = c("sI","tI", "rho"))

df_zetaI_vis_by_tI$zetaI <- zetaI.2o(df_zetaI_vis_by_tI$sI,
                                df_zetaI_vis_by_tI$tI,
                                df_zetaI_vis_by_tI$rho)

df_zetaI_vis_by_tI$tI <- as.factor(df_zetaI_vis_by_tI$tI)
df_zetaI_vis_by_tI$rho <- as.factor(df_zetaI_vis_by_tI$rho)
```



```{r}
df_zetaI_vis_by_tI$phi_sI <-  phi(df_zetaI_vis_by_tI$sI)
df_zetaI_vis_by_tI$phi_zetaI <-  phi(df_zetaI_vis_by_tI$zetaI)
```


```{r, fig.width=11, fig.height = 4.5}
palette_few_tI <- sequential_hcl(length(tI_zetaI_vis)*1.3, "Blues 3", rev = T)
length(palette_few_tI)
palette_few_tI <- palette_few_tI[(length(palette_few_tI)-length(tI_zetaI_vis)):length(palette_few_tI)] # we need to subset it to get along
length(palette_few_tI)


pl_2o_zetaI_by_tI_phi <- ggplot(df_zetaI_vis_by_tI,aes(phi_sI,phi_zetaI, colour = tI)) + 
                        geom_line(size = lsize) +
                        scale_y_continuous(name = axis_name_phi_zeta, limits = c(.6,1)) +
                        scale_x_continuous(name = axis_name_initial_acc) +
                        scale_color_manual(values = palette_few_tI) + 
                        facet_wrap(.~rho)
pl_2o_zetaI_by_tI_phi
```


## Joining the two together

```{r, fig.width=11, fig.height = 10}
pl_zetaI_large <- pl_2o_zetaI_by_rho_phi + pl_2o_zetaI_by_tI_phi + plot_layout(ncol = 1) & guides(colour = "none")
pl_zetaI_large
```

```{r}
ggsave(file = "output/MetaSearch_app_zeta.pdf",
       plot = pl_zetaI_large,
       device = cairo_pdf,
       width = 11,
       height = 10,
       units = "in",
       dpi = 300)
```

