---
title: "Additional Model Analysis & Data"
output: html_notebook
---

# About

This file produces additional figures for the results section and appendix:
* Results:
  * Fig. 7: Metacognitive accuracy in search
  * Fig. 9: Simulations and trial by trial analysis of data
  * Fig. 10: Over- and underconfidence in model and data
* Appendix:
  * Fig. B1 and B2: Additional data analysis

# Set-up

We load the necessary libraries and functions

```{r}
source("backend/global_all.R")

source("backend/data_analysis/metaSTD_functions.R")
source("backend/data_analysis/data_analysis_functions.R")
source("backend/models/simulations/simulation_functions.R")
source("backend/models/secondorder/model_2o_subjective.R")
source("backend/global_settings.R")

source("backend/hmetad/Function_metad_indiv.R")
source("backend/hmetad/hmeta_d_wrapper_functions.R")

base_size <- 15
theme_set(theme_classic(base_size = base_size))

compute_standard_error <- function(x) sd(x)/sqrt(length(x))
```

We add the libraries 

```{r}
library(patchwork)
library(ggnewscale)
library(scales)
library(viridis)
library(RColorBrewer)
library(colorspace)
library(arm)
library(ggpubr)
library(tidyverse)
library(msm)
library(afex)
library(arm)
library(conflicted)
library(rjags)
library(magrittr)

conflict_prefer("select", "dplyr")
conflict_prefer("filter","dplyr")
```



# Fig. 7: Additional theory - Metacognitive search sensitivity

We first produce the figure showing metacognitive search sensitivity as a function of sigma_I and rho_I. 

We first set the relevant parameters

```{r}
sI_set <- seq(1,3, by = .5)
tI_set <- sI_set
sigma_tau_expand <- expand.grid(sI_set, tI_set)
```

## Postdecisional model

```{r}
set.seed(22)

df_for_sensitivity.Pd <- get_simulated_df_with_search_and_meta_metrics(
  sigma_tau_expand[,1],
  sigma_tau_expand[,2],
  sI_subj_vector = FALSE,
  sF_fix = 1,
  rS_fix = -.1,
  model = "Pd",
  n_total_simulations = 100000,
  compute_meta_d = FALSE
)
```

## Second-order model

```{r}
df_for_sensitivity.2o <- get_simulated_df_with_search_and_meta_metrics(
  sigma_tau_expand[,1],
  sigma_tau_expand[,2],
  sI_subj_vector = FALSE,
  rho_fix = 0.3,
  sF_fix = 1,
  rS_fix = -.1,
  model = "2o",
  compute_meta_d = FALSE
)
```

## Plotting

### Function for plotting

```{r}
plot_search_sensitivty <- function(df, model = "2o"){
  
  df <-  df %>% 
    mutate(sI = as.factor(sI))
  
  if (model == "2o") {
    plot <- df %>% 
      ggplot(aes(tI, search_ratio, colour = sI, group = sI)) 
  } else if (model == "Pd"){
    plot <- df %>% 
      ggplot(aes(tI, search_ratio_empirical, colour = sI, group = sI)) 
  }
  
  plot <- plot + 
      geom_point(size = psize) +
      geom_line(size = lsize) +
      scale_x_continuous(name = bquote(tau[I]),
                         breaks = 1:3,
                         limits = c(.8,3.2)) + 
      scale_y_continuous(name = "Search Sensitivity",
                         limits = c(0,2.5),
                         breaks = 0:2) +
      geom_hline(yintercept = 0,
                 alpha= .5,
                 linetype = "dashed") +
      scale_color_manual(name = bquote(sigma[I]),
                         values = rev(palette_for_sigma[1:5])) 
  
  return(plot)
}

pl_sensitivity.2o <- plot_search_sensitivty(df_for_sensitivity.2o)
pl_sensitivity.2o
```

### Model plots

```{r}
pl_sensitivity.Pd <- plot_search_sensitivty(df_for_sensitivity.Pd, model = "Pd") +
  guides(colour = "none")
pl_sensitivity.Pd
pl_sensitivity.2o <- plot_search_sensitivty(df_for_sensitivity.2o)
pl_sensitivity.2o
```

### Example plots

```{r}
dodged_position <- position_dodge(0.2)

df_search_ratio_example <- 
  data.frame(
    mock_id = 1,
    correctness = c("Incorrect", "Correct"),
    search = c(0.8, .3)
  )

pl_search_ratio_example_bars <- df_search_ratio_example %>% 
  mutate(correctness = fct_rev(correctness)) %>%
  ggplot(aes(x = correctness, y = search)) +
    geom_col(aes(fill = correctness), 
               position = dodged_position,
               # colour = "black",
             alpha = .9) +  
    scale_fill_manual(values = c(colour$distribution_incorrect, colour$distribution_correct)) +
    guides(colour = "none") +
    scale_x_discrete(name = "Initial Accuracy") +
    scale_y_continuous(name = "Av. Search",
                       limits = c(0,1),
                       breaks = 0:2/2,
                       expand = c(0,0)) +
    guides(fill = "none")
pl_search_ratio_example_bars
```

### Full plot

```{r, fig.height= 4, fig.width=8.2}
pl_search_sensitivity_joint <- pl_search_ratio_example_bars + pl_sensitivity.Pd + pl_sensitivity.2o + plot_layout(widths = c(1.2,1.5,1.5))
pl_search_sensitivity_joint
```

Saving this plot

```{r, fig.height= 4, fig.width=8.2}
ggsave(file = "output/MetaSearch_search_efficiency_2.pdf",
       plot = pl_search_sensitivity_joint,
       device = "pdf",
       width = 8.2,
       height = 4,
       units = "in",
       dpi = 300)
```


# Fig's 7 and 9: Data Plus Theory Section

## Load and prep data from Schulz et al. (2020)

Here, we can either do the entire preprocessing here or load an existing fit. 


```{r}
data_processing_setting <- "load"

if(data_processing_setting == "run"){
  
  df_s1 <- read.csv(file = "data/raw/S1_TaskData.csv", header = TRUE) # Task Data
  df_s2 <- read.csv(file = "data/raw/S2_TaskData.csv", header = TRUE) # Task Data
  df_complete <- rbind(df_s1,df_s2)
  
  df_add_s1 <- read.csv(file = "data/raw/S1_Add.csv", header = TRUE)
  df_add_s2 <- read.csv(file = "data/raw/S2_Add.csv", header = TRUE)
  df_add_complete <- rbind(df_add_s1, df_add_s2)
  
  ids <- unique(df_complete$ID)
  length(ids)
  
  
  df_complete[which(df_complete$Confidence1st == 67),]$Confidence1st <- 1
  df_complete[which(df_complete$Confidence1st == 83),]$Confidence1st <- 2
  df_complete[which(df_complete$Confidence1st == 100),]$Confidence1st <- 3
  df_complete[which(df_complete$Confidence2nd == 67),]$Confidence2nd <- 1
  df_complete[which(df_complete$Confidence2nd == 83),]$Confidence2nd <- 2
  df_complete[which(df_complete$Confidence2nd == 100),]$Confidence2nd <- 3
  
  
  df_compleSte <- df_complete %>% 
    mutate(Confidence1st = as.factor(Confidence1st),
           Confidence2nd = as.factor(Confidence2nd))
  
  df_meta <- get_averages_and_meta_stats(df_complete, df_add_complete, 
                                        fit_type = "hmetad", hmetad_seed = 20)
  
  # write.csv(x = df_meta, "data/processed/df_meta_hmetad_seed20.csv")
  
  
} else if(data_processing_setting == "load") {
  
  df_meta <- read.csv("data/processed/df_meta_hmetad_seed20.csv")
}


```


```{r}
ids_with_intermediate_search <- df_meta %>% 
  filter(mean_search >= 0.05 & mean_search <= 0.95)
ids_with_intermediate_search <- as.vector(unique(ids_with_intermediate_search$ID))

df_intermediate_search <- df_complete %>% 
  filter(ID %in% ids_with_intermediate_search)

length(ids_with_intermediate_search)

```

## Trial-by-trial effects (Fig. 9)

### Model

#### Search by cost and confidence curves

First, we get the components from a model

```{r}
df_components <- model.2o(1.25,1.25,0.5,1,0, output = "components")

df_components <- rbind(df_components, df_components)
df_components$rS <- rep(c(-.05, -.2), each = nrow(df_components)/2)
df_components$Q_difference <- df_components$Q1 + df_components$rS - df_components$Q0
```


We then compute a choice probability based on this

```{r, fig.height=3.5, fig.width=4}
softmax_temp <- 20

df_components$choice_p <- sigmoid(20*df_components$Q_difference)

pl_choice_probabilities_with_label <- df_components %>%
  filter(cI > 0.5) %>% 
  mutate(rS = as.factor(rS * 100),
         rS = fct_rev(rS)) %>% 
  ggplot(aes(cI, choice_p, colour = as.factor(rS), fill = as.factor(rS))) +
    geom_area(position = "identity", alpha = .1) +
    geom_line(size = lsize) +
  guides(fill = "none") +
    scale_color_manual(values = palette_4costs[c(2,4)], name = bquote(r[S])) +
    scale_fill_manual(values = palette_4costs[c(2,4)], name = bquote(r[S])) +
    scale_x_continuous(name = bquote(c[I])) +
    scale_y_continuous(name = "Probability of Search",
                       breaks = c(0, .5, 1))


pl_choice_probabilities <- pl_choice_probabilities_with_label + guides(color = "none", fill = "none")
pl_choice_probabilities
```

```{r}
pl_choice_probabilities_with_label
```

```{r}
ggsave(file = "output/final/MetaSearch_confcost_simulation.pdf",
       plot = pl_choice_probabilities_with_label,
       device = "pdf",
       width = 4,
       height = 4,
       units = "in",
       dpi = 300)
```


#### Sensitivity plot

##### Simulations

```{r}
run_sensitivity_plot_sim <- FALSE

if (run_sensitivity_plot_sim) {
  example_seed <- 297
  set.seed(example_seed)
  n_overunder_sim <- 150
  
  performance_objective <-  runif(n_overunder_sim, .6, .85) 
  performance_subjective <- runif(n_overunder_sim, .6, .85) 
  performance_tau <- runif(n_overunder_sim, .6, .85) 
  
  sigma_is_subjective <- 1/qnorm(performance_subjective) 
  sigma_is_objective <- 1/qnorm(performance_objective) 
  tau_is <- 1/qnorm(performance_tau)
  
  df_overunderconf <- get_simulated_df_with_search_and_meta_metrics(
    sI_vector = sigma_is_objective, 
    tI_vector = tau_is,
    sI_subj_vector = sigma_is_subjective, 
    rho_fix = 0.3,
    sF_fix = 1,
    rS_fix = -.1,
    model = "2o",
    n_total_simulations = 500,
    compute_meta_d = TRUE,
    pad_factor = 0,
    meta_d_fit_type = "hmetad",
    hmetad_seed = 1
  )
}

```


```{r}
# filename_sim_df <- paste0("data/simulations/df_overunderconf_n_", n_overunder_sim, "_seed_", example_seed, "_1.csv")
# write.csv(df_overunderconf, filename_sim_df)
```

```{r}
df_overunderconf <- read.csv("data/simulations/df_overunderconf_n_150_seed_297_1.csv")
```


##### Plot

We  write a function that does the sensitivity plots

```{r}
plot_sensitivity_plots <- function(df, scatter = "meta-d", 
                                   ratio_axis_limits = c(-2,4),
                                   meta_d_axis_limits = c(0,4),
                                   bin_width = 40){
  
  pl_conditional_boxplot <- df %>% 
    pivot_longer(cols = c("av_search_correct_empirical", "av_search_incorrect_empirical"), 
                 names_to = "Correctness",
                 values_to = "conditional_search") %>% 
    mutate(Correctness = fct_rev(Correctness)) %>% 
    ggplot(aes(Correctness, conditional_search, fill = Correctness)) +
      geom_boxplot(size = 1)  +
      scale_fill_manual(values = c(colour$distribution_incorrect,colour$distribution_correct)) +
      guides(fill = "none") +
      scale_x_discrete(name = "Initial Accuracy", labels = c("Incorrect", "Correct")) +
      scale_y_continuous(name = "Av. Search", limits = c(0,1)) 
  # pl_conditional_boxplot
  
  
  
  pl_search_ratio_distribution <- df %>% 
    ggplot(aes(search_ratio_empirical)) + 
      geom_histogram(binwidth = bin_width,
                     fill = "lightgrey",
                      colour = "black") +
      scale_y_continuous(name = "Count", breaks = c(0,10),
                         expand = c(0,0)) +
      scale_x_continuous(name = "Search Sensitivity",
                         limits = ratio_axis_limits) +
      geom_vline(xintercept = 0,
                 alpha = .5,
                 linetype = "dashed")  +
      coord_flip() 

  pl_search_ratio_by_meta_d_grey <- df %>% 
    ggplot(aes(meta_da, search_ratio_empirical, colour = tI)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE,
                  colour = "black")  +
      geom_hline(yintercept = 0,
                 alpha= .5,
                 linetype = "dashed") +
      scale_x_continuous(name = "meta-d'") +
      scale_y_continuous(name = "Search Sensitivity") +
      coord_cartesian(ylim = ratio_axis_limits,
                      xlim = meta_d_axis_limits) +
      scale_fill_continuous_sequential(palette = "Blues",
                                       end = 1, begin = .15,
                                       name = bquote(tau[I])) +
      scale_colour_continuous_sequential(limits = c(0.8,4.2),palette = "Blues",
                                       end = 1, begin = .23,
                                       name = bquote(tau[I]))

  pl_search_ratio_by_M_ratio_grey <- df %>% 
    ggplot(aes(M_ratio, search_ratio_empirical, fill = sI_by_tI)) +
      geom_point(colour = "black",
                 shape = 21) +
      geom_smooth(method = "lm", se = FALSE,
                  colour = "black")  +
      geom_hline(yintercept = 0,
                 alpha= .5,
                 linetype = "dashed") +
    coord_cartesian(ylim = ratio_axis_limits,
                    xlim = meta_d_axis_limits) +
    scale_fill_continuous_divergingx(palette = "Geyser",
                                 name = bquote(sigma[I]*"/"*tau[I]),
                                 # limits = c(0.50, 1.5),
                                 mid = 1)

  if (scatter == "meta-d") pl_scatter <- pl_search_ratio_by_meta_d_grey
  if (scatter == "M-ratio") pl_scatter <- pl_search_ratio_by_M_ratio_grey

  plot_array <- (pl_conditional_boxplot | 
                   pl_search_ratio_distribution | 
                   pl_scatter) +
    plot_layout(widths = c(1,.7,1.7))
  
  return(plot_array)
}
```

We combine this plot with the plot choice probability plot


```{r, fig.width= 12, fig.height= 4}
pl_model_sensitvity_large <- 
  (pl_choice_probabilities + 
   plot_sensitivity_plots(df_overunderconf, 
                          meta_d_axis_limits = c(-.5,3.2),
                          ratio_axis_limits = c(-1.4,3.3),
                          scatter = "meta-d", bin_width = .1)) + 
    plot_layout(widths = c(1.7,4))
pl_model_sensitvity_large
```

## Data

### Effects of confidence and cost on search

We make the plot

```{r, fig.height=3.5, fig.width=5}
pl_confidence_cost <- df_intermediate_search %>% 
  group_by(ID, Confidence1st, InfoCost) %>% 
  summarise(avg_info_seek = mean(SeeAgain)) %>% 
  ggplot(aes(x = as.factor(Confidence1st), y = avg_info_seek, 
             colour = as.factor(InfoCost),
             fill = as.factor(InfoCost))) +
    geom_boxplot(size = 1,
                 outlier.shape = NA) +
    scale_colour_manual(values = rep("black",2)) +  #palette_4costs[c(1,3)], name = "Cost"s) +
    scale_fill_manual(values = palette_4costs[c(1,3)], name = bquote(r[S])) +
    scale_y_continuous(breaks = c(0, .5, 1)) + 
    guides(colour = "none") + 
    labs(x = "Initial Confidence Level",
         y = "Av. Search") 
pl_confidence_cost
```

```{r}
ggsave(file = "output/final/MetaSearch_confidence cost.pdf",
       plot = pl_confidence_cost,
       device = "pdf",
       width = 7.75,
       height = 4,
       units = "in",
       dpi = 300)
```


We analyse this

```{r}
df_intermedia_search_for_analysis <- df_intermediate_search %>% 
  mutate(Confidence1st = as.numeric(Confidence1st) -2,
         InfoCost = ifelse(InfoCost == 5, 0, 1))
```

```{r}
m_seek_by_conf_cost_rslope <- mixed(SeeAgain ~ Confidence1st + InfoCost +
                        (Confidence1st + InfoCost|ID), 
                        data = df_intermedia_search_for_analysis, 
                        family = binomial,
                        method = "LRT",
                        nAGQ = 0)
anova(m_seek_by_conf_cost_rslope)
summary(m_seek_by_conf_cost_rslope)
```

### Effects of accuracy on search

We make the plot

```{r, fig.height=3.5, fig.width=3}
pl_within_accuracy <- df_intermediate_search %>%
  mutate(Correct1st = as.factor(Correct1st)) %>% 
  group_by(ID, Correct1st) %>% 
  summarise(avg_info_seek = mean(SeeAgain)) %>% 
  ggplot(aes(x = Correct1st, y = avg_info_seek, fill = Correct1st)) +
    geom_boxplot(size = 1) +
    scale_fill_manual(values = c(colour$distribution_incorrect,colour$distribution_correct)) +
    guides(fill = "none") +
    scale_x_discrete(name = "Initial Accuracy", labels = c("Incorrect", "Correct")) +
    scale_y_continuous(name = "Av. Search")
pl_within_accuracy
```


We run the analysis

```{r}
m_seek_by_correct <- mixed(SeeAgain ~ Correct1st +
                        (Correct1st|ID), 
                        data = df_intermedia_search_for_analysis, 
                        family = binomial,
                        method = "LRT",
                        nAGQ = 0)
anova(m_seek_by_correct)
summary(m_seek_by_correct)
```


### Search Sensitivity

#### Compute search sensitivity from data

```{r}
df_search_ratios <- df_intermediate_search %>% 
  mutate(Correct1st = as.factor(Correct1st),
         Correct1st = ifelse(Correct1st == 1, "correct", "incorrect")) %>% 
  group_by(ID, Correct1st) %>%
  summarize(mean_search = mean(SeeAgain)) %>% 
  pivot_wider(id_cols = "ID",
              names_from = "Correct1st",
              names_prefix = "search_",
              values_from = "mean_search")

df_search_ratios <- merge(df_meta,
                                  df_search_ratios)

df_search_ratios <- df_search_ratios %>% 
  mutate(search_ratio =  (search_incorrect - search_correct) / mean_search)

df_search_ratios
```

We probe the number of participants with search sensitivty larger than 0

```{r}
df_search_ratios %>% 
  mutate(search_ratio_greater_0 = ifelse(search_ratio > 0, TRUE, FALSE)) %>% 
  count(search_ratio_greater_0) %>% 
  mutate(percent = n / sum(n))
```

#### Plots of search sensitivity

We first plot the distribution

```{r}
pl_search_ratio_distribution <- df_search_ratios %>% 
  ggplot(aes(search_ratio)) + 
    geom_histogram(binwidth = .1,
                     fill = "lightgrey",
                      colour = "black") +
    scale_y_continuous(name = "Count", expand = c(0,0)) +
    scale_x_continuous(name = "Search Sensitivity") +
    geom_vline(xintercept = 0,
               alpha = .5,
               linetype = "dashed")  +
    coord_flip() 
    
pl_search_ratio_distribution
```

And then the scatter plots

```{r}
pl_seekratio_metad <- df_search_ratios %>% 
  #filter(meta_dprime > -.5) %>% 
  ggplot(aes(meta_dprime, search_ratio)) +
    geom_point(fill = "lightgrey",
               colour = "black",
               shape = 21) +
    geom_smooth(method = "lm", se = FALSE,
                colour = "black")  +
    scale_y_continuous(name = "Search Sensitivity") +
    scale_x_continuous(name = "meta-d'") +
    geom_hline(yintercept = 0,
               alpha= .5,
               linetype = "dashed") +
    stat_cor(method = "pearson")
pl_seekratio_metad
```

And then make the full plot

```{r, fig.width= 12, fig.height= 4}
pl_data_sensitivity_large <- 
  (pl_confidence_cost + guides(fill = "none") | pl_within_accuracy |  pl_search_ratio_distribution | pl_seekratio_metad) +
    plot_layout(widths = c(1.7, 1,.7,1.7))

pl_data_sensitivity_large
```

We also run the correlation anaylsis

```{r}
cor.test(df_search_ratios$meta_dprime, df_search_ratios$search_ratio)
```


## Full trial-by-trial results

```{r, fig.width= 13, fig.height= 8}
pl_within_results_joint <- pl_model_sensitvity_large / pl_data_sensitivity_large
pl_within_results_joint
```


```{r}
ggsave(file = "output/final/MetaSearch_within_results.pdf",
       plot = pl_within_results_joint,
       device = "pdf",
       width = 13,
       height = 8,
       units = "in",
       dpi = 300)
```


# Fig. 10: Task averages with over and underconfidence

## Simulations

### Scatterplots

```{r, fig.height= 8, fig.width= 17}
simulation_point_shape <- 21
simulation_point_size <- 2.5

pl_accuracy_confidence <- df_overunderconf %>% 
  ggplot(aes(av_correct, av_confidence, fill = sigma_difference)) +
    geom_point(colour = "black",
               size = simulation_point_size,
               shape = simulation_point_shape) +
    # geom_smooth(method = "lm", colour = "black") +
    scale_y_continuous(name = "Av. Confidence",
                       limits = c(.57, .87))+
    scale_x_continuous(name = axis_name_initial_acc,
                       limits = c(.57, .87)) +
    scale_fill_continuous_divergingx(name = 
                                    bquote(sigma["I"]*" - "*sigma["I"]), # adding to second R,
                                     palette = "PuOr",
                                     breaks = c(-2,0,2)) +
    geom_abline(alpha = .3, linetype = "dashed") +
    coord_fixed() 


pl_accuracy_search <- df_overunderconf %>% 
  ggplot(aes(av_correct, av_search)) +
    geom_point(aes(fill = sigma_difference),
               colour = "black",
               size = simulation_point_size,
               shape = simulation_point_shape) +
    geom_smooth(method = "lm",
                colour = "black") +
    scale_y_continuous(name = "Av. Search",
                       limits = c(-.03, 1.03),
                       breaks = c(0,.5,1))+
    scale_x_continuous(name = axis_name_initial_acc,
                       limits = c(.57, .87)) +
    scale_fill_continuous_divergingx(name = 
                                     bquote(sigma["I, obj"]*" - "*sigma["I, subj."]),
                                   palette = "PuOr",
                                   breaks = c(-2,0,2)) + 
    guides(fill = "none")


pl_confidence_search <- df_overunderconf %>% 
  ggplot(aes(av_confidence, av_search)) +
    geom_point(aes(fill = sigma_difference),
                   colour = "black",
                   size = simulation_point_size,
                   shape = simulation_point_shape) +
    geom_smooth(method = "lm",
                colour = "black") +
    scale_y_continuous(name = "Av. Search",
                       limits = c(-.03, 1.03),
                       breaks = c(0,.5,1)) +
    scale_x_continuous(name = "Av. Confidence",
                       breaks = c(0.6, 0.7, 0.8),
                       limits = c(.6, .87)) +
    scale_fill_continuous_divergingx(name = 
                                   bquote(sigma["I, obj"]*" - "*sigma["I, subj."]),
                                 palette = "PuOr",
                                 breaks = c(-2,0,2)) + 
    guides(fill = "none")

pl_metaefficiency_search <- df_overunderconf %>% 
  ggplot(aes(M_ratio, av_search)) +
    geom_point(aes(fill = sigma_difference),
                   colour = "black",
                   size = simulation_point_size,
                   shape = simulation_point_shape) +
    scale_fill_continuous_divergingx(name = 
                                 bquote(sigma["I, obj"]*" - "*sigma["I, subj."]),
                               palette = "PuOr",
                               breaks = c(-2,0,2)) + 
    geom_point(colour = "black",
             fill =  "lightgrey",
             shape = 21) +
    geom_smooth(method = "lm",
                colour = "black") +
    scale_y_continuous(name = "Av. Search",
                       limits = c(-.03, 1.03),
                       breaks = c(0,.5,1))+
    scale_x_continuous(name = "M-ratio")  + # bquote(sigma["I,objective"]*"/"*tau[I])

        geom_point(colour = "black",
                 fill =  "lightgrey",
                 shape = 21) +
    geom_vline(xintercept = 1, alpha = .3, linetype = "dashed") +
    # lims(x = c(0,2.5))
    guides(fill = "none")

pl_meta_d_search <- df_overunderconf %>% 
  ggplot(aes(meta_da, av_search)) +
    geom_point(aes(fill = sigma_difference),
                   colour = "black",
                   size = simulation_point_size,
                   shape = simulation_point_shape) +
    scale_fill_continuous_divergingx(name = 
                                 bquote(sigma["I"]*" - "*sigma["I"]), # adding to second R
                               palette = "PuOr",
                               breaks = c(-2,0,2)) + 
    geom_smooth(method = "lm",
                colour = "black") +
    scale_y_continuous(name = "Av. Search",
                       limits = c(-.03, 1.03),
                       breaks = c(0,.5,1))+
    scale_x_continuous(name = "meta-d'") +
    guides(fill = "none")

pl_meta_d_search
```

We plot this together

```{r, fig.height= 4, fig.width= 17}
pls_averages <- (pl_accuracy_confidence | pl_accuracy_search | pl_confidence_search | pl_meta_d_search) &
    theme_classic(base_size = 20) # + plot_annotation(tag_levels = 'A') 
pls_averages
```

```{r}
ggsave(file = "output/final/MetaSearch_average_results.pdf",
       plot = pls_averages,
       device = "pdf",
       width = 17,
       height = 4,
       units = "in",
       dpi = 300)
```

### Regression

#### Run regression

```{r}
df_overunderconf_scaled <- df_overunderconf %>% 
  mutate(av_search = scale(av_search),
         av_correct = scale(av_correct),
         av_confidence = scale(av_confidence),
         meta_da = scale(meta_da),
         M_ratio = scale(M_ratio)
  )

m_search_by_all_metad <- lm(av_search ~ av_correct + av_confidence + meta_da, 
                      df_overunderconf_scaled)
m_search_by_all_metad <- summary(m_search_by_all_metad)
m_search_by_all_metad

# Get data ready for the regression
df_av_search_regression_metad <- data.frame(m_search_by_all_metad$coefficients)
df_av_search_regression_metad
df_av_search_regression_metad$parameter <- c("Intercept","Av. Accuracy", "Av. Confidence", "meta-d'")
```

#### Plot regression

```{r, fig.height= 4, fig.width= 12}
plot_regression <- function(df, 
                            y_limits = c(-.35,.35),
                            order_vector = c(2,1,3)
                            ){
  
  regressor_order <- c("Av. Confidence","Av. Accuracy", "meta-d'")
  regressor_order <- regressor_order[order_vector]
  regressor_labels <-  c("Average\nConfidence", "Average\nAccuracy", "meta-d'")
  regressor_labels <- regressor_labels[order_vector]
  regressor_palette <- c(palette_for_sigma[3],
                         divergingx_hcl(5, "PuOr")[4],
                         palette_5taus[2])
  
  # regressor_palette <- c( #palette_for_sigma[3], 
  #                        rep("grey",3))
  regressor_palette <- regressor_palette[order_vector]
  
  regressor_palette <- 
  
  
  pl_regression <- df %>% 
    filter(parameter != "Intercept") %>% 
    mutate(parameter = fct_relevel(parameter, regressor_order)) %>% 
    ggplot(aes(parameter, Estimate, fill = parameter)) +
      geom_col(width = .7, colour = "black") +
      geom_errorbar(aes(ymin = Estimate - Std..Error,
                        ymax = Estimate + Std..Error),
                    width = .2) +
      geom_hline(yintercept = 0) +
      guides(fill = "none") +
      scale_y_continuous(
        name = bquote('Standardized ' * beta),
        limits = y_limits
      ) +
      scale_x_discrete(name = "Predictors of Av. Search",
                       labels = regressor_labels) +
      scale_fill_manual(values = regressor_palette) +
      theme_classic(base_size = 20)
      
  return(pl_regression)
}
```

```{r}
pl_model_regression <- plot_regression(df = df_av_search_regression_metad,
                y_limits = c(min(df_av_search_regression_metad$Estimate - .15),.4))
```

## Data

### Correlations

```{r}
cor.test(df_meta$mean_accuracy, df_meta$mean_confidence)
```

```{r}
cor.test(df_meta$mean_search, df_meta$mean_confidence)
cor.test(df_meta$mean_search, df_meta$mean_accuracy)
cor.test(df_meta$mean_search, df_meta$meta_dprime)
```

### Run regression

We run the regression

```{r}
df_meta_scaled <- df_meta %>% 
  # filter(ID %in% ids_with_intermediate_search) %>% 
  mutate(mean_search = scale(mean_search),
         mean_accuracy = scale(mean_accuracy),
         mean_confidence = scale(mean_confidence),
         meta_dprime = scale(meta_dprime),
         mratio = scale(mratio),
         MaxPoints = scale(MaxPoints),
         AccStronger = scale(AccStronger),
         mean_final_accuracy = scale(mean_final_accuracy)
         )


m_search_by_all <- lm(mean_search ~ mean_accuracy + mean_confidence  +  meta_dprime, df_meta_scaled)
m_search_by_all <- summary(m_search_by_all)
m_search_by_all
```


### Plot the regression

We get the regression ready for plotting

```{r}
df_av_search_regression <- data.frame(m_search_by_all$coefficients)
df_av_search_regression
df_av_search_regression$parameter <- c("Intercept","Av. Accuracy", "Av. Confidence", "meta-d'")

pl_data_regression <- plot_regression(df_av_search_regression,
                                      y_limits = c(min(df_av_search_regression_metad$Estimate - .15),.4))
```

## Joint regression plot: data & simulations

```{r, fig.height= 4, fig.width= 12}
pls_regression <- pl_model_regression + pl_data_regression  & 
  theme_classic(base_size = 20)
pls_regression
```

```{r}
ggsave(file = "output/final/MetaSearch_regressions.pdf",
       plot = pls_regression,
       device = "pdf",
       width = 12,
       height = 4,
       units = "in",
       dpi = 300)
```

# Appendix: More results

## Data

### Distribution of meta-d and da

```{r}
pl_meta_distribution <- df_meta %>% 
  ggplot(aes(dprime, meta_dprime, colour = mratio)) +
    geom_point() +
    geom_abline(linetype = "dashed") +
    # geom_smooth(method = "lm", colour = "black") +
    coord_fixed() +
    scale_colour_viridis(name = "M-ratio", limits = c(min(df_meta$mratio),max(df_meta$mratio)),option = "D", begin = 0) +
    scale_x_continuous(name = "d'", limits = c(-.5,3)) + 
    scale_y_continuous(name = "meta-d'")

pl_meta_distribution
```


```{r}
ggsave(file = "output/MetaSearch_meta_da_and_da_distributions.pdf",
       plot = pl_meta_distribution,
       device = cairo_pdf,
       width = 6,
       height = 4,
       units = "in",
       dpi = 300)
```


### Final accuracy


```{r, fig.width=6, fig.height=4}
pl_data_final_acc <- df_meta %>% 
  ggplot(aes(mean_final_accuracy, mean_accuracy, colour = mean_search)) +
    geom_abline(linetype = "dashed") +
    # geom_point() +
    geom_jitter(width = .003, height = .003) + 
    scale_colour_continuous_sequential(palette = "inferno",rev = FALSE,
                                       end = .9,
                                       begin = 0.25,
                                       name = "Av. Search",
                                       breaks = c(0,.5,1)) +
    scale_y_continuous(limits = c(0.6,.85),
                       breaks = c(0.6,.7,.8),
                       name = "Av. Initial Accuracy") +
    scale_x_continuous(name = "Av. Final Accuracy",
                       breaks = c(0.5, 0.75, 1))
 
```


```{r}
ggsave(file = "output/MetaSearch_data_final_acc.pdf",
       plot = pl_data_final_acc,
       device = cairo_pdf,
       width = 6,
       height = 4,
       units = "in",
       dpi = 300)
```
