---
title: "Introduction"
author: "Lion Schulz"
output: html_notebook
---

# Notebook purpose

This notebook contains the code for the computations part.

# Set-up

We load the back-end

```{r}
source("backend/global_all.R")
```

# Figure 1: Distributions

We set some parameters




## Postdecisional Figure

```{r}
# Set-up
resolution_fig1 <- 100
sigint <- c(-10,10)
XI_vector <- seq(from = sigint[1], to = sigint[2], length.out =  resolution_fig1)
YI_vector <- XI_vector

# Postdecisional figure
sI_fig1.Pd <- 2
tI_fig1.Pd <- 1.5
rho.Pd <- 0

Sigma_I.Pd <- computeCov(sI_fig1.Pd,tI_fig1.Pd,rho.Pd)
XIYI_matrix <- expand.grid(XI_vector,YI_vector)
density_XIYI_matrix <- matrix(dmvnorm(XIYI_matrix,mean = c(1,1),sigma = Sigma_I.Pd),nrow = length(XI_vector))

df_2o_Isource <- melt(density_XIYI_matrix)
df_2o_Isource$XI <- XI_vector[df_2o_Isource$Var1]
df_2o_Isource$XF <- YI_vector[df_2o_Isource$Var2]
```


```{r}
# Setting for the figure
fig1_xy_breaks_distributions <- c(-5,0,5) 
distribution_lsize <- 2
distribution_alpha <- .7
# deliniating the seeking polygon
dpoly <- data.frame(x = c(4.25,5.75,-5,-5), y = c(-5,-5,5.75,4.25))


# Figure
pl_distribution.Pd <- ggplot(df_2o_Isource, aes(x = XI, y = XF)) + 
  geom_polygon(data = dpoly, aes(x = x, y = y),
               fill = "grey") + 
  geom_contour(data = df_2o_Isource,
               aes(x = XI, y = XF, z=value), colour = "black",
               size = distribution_lsize -.5,
               alpha = distribution_alpha) + 
  labs(x=bquote(X["I"]), y=bquote(Y["I"])) +
  coord_cartesian(xlim = c(-5,5), ylim = c(-5,5)) +
  scale_x_continuous(breaks = fig1_xy_breaks_distributions,
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(breaks = fig1_xy_breaks_distributions,
                     labels = scales::number_format(accuracy = 0.1))
pl_distribution.Pd
```

# Second order figure

```{r}
sI_fig1.2o <- 2
tI_fig1.2o <- 1.5
roh_distribution.2o <- .7

Sigma_I <- computeCov(sI_fig1.2o,tI_fig1.2o,roh_distribution.2o)
density_XIYI_matrix <- matrix(dmvnorm(XIYI_matrix,mean = c(1,1),sigma = Sigma_I),nrow = length(XI_vector))

df_2o_Isource <- melt(density_XIYI_matrix)
df_2o_Isource$XI <- XI_vector[df_2o_Isource$Var1]
df_2o_Isource$XF <- YI_vector[df_2o_Isource$Var2]

## and with the seeking zone
pl_distribution.2o <- ggplot(df_2o_Isource, aes(x = XI, y = XF)) + 
  geom_rect(xmin = -5,
            xmax = 0,
            ymin = -.75,
            ymax = .25,
            fill = "grey") +
  geom_rect(xmin = 0,
            xmax = 5,
            ymin = -.25,
            ymax = .75,
            fill = "grey") +
  geom_contour(data = df_2o_Isource,
               aes(x = XI, y = XF, z=value), colour = "black",
               size = distribution_lsize -.5,
               alpha = distribution_alpha) + labs(x=bquote(X["I"]), y=bquote(Y["I"])) +
  coord_cartesian(xlim = c(-5,5), ylim = c(-5,5)) +
  scale_x_continuous(breaks = fig1_xy_breaks_distributions,
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(breaks = fig1_xy_breaks_distributions,
                     labels = scales::number_format(accuracy = 0.1)) 
pl_distribution.2o
```

```{r}
vertical_line_size <- 1
pls_distributions <- pl_distribution.Pd + pl_distribution.2o & geom_vline(xintercept = 0, size =vertical_line_size)
pls_distributions
```


# Confidences

## Postdecisional confidence

```{r}
zetaI.Pd <- 2

cI.Pd_plus <- sigmoid(2*XI_vector/zetaI.Pd^2)
cI.Pd_minus <- 1 - cI.Pd_plus
```

```{r}
df_cI.Pd <- data.frame(ZI = XI_vector,
                       cI_plus = cI.Pd_plus,
                       cI_minus = cI.Pd_minus)
df_cI.Pd <- melt(df_cI.Pd, id.vars = "ZI")
```

```{r}
confidence_breaks <- c(0,.5,1)

confidence_lsize <- 2

plot_pd_conf <- ggplot(df_cI.Pd, aes(x = ZI, y = value, colour = variable)) + 
  geom_line(size = confidence_lsize) +
  coord_cartesian(xlim = c(-5,5), ylim = c(0,1)) +
  scale_x_continuous(breaks = fig1_xy_breaks_distributions,
                     name = bquote(Z[I]),
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(breaks = confidence_breaks,
                     name = "Confidence",
                     labels = scales::number_format(accuracy = 0.1)) + 
  geom_vline(xintercept = 0,
             size = vertical_line_size) +
  geom_hline(yintercept = .5,
             linetype = "dashed",
             size = vertical_line_size) +
  scale_color_manual(values = palette_2ais) + guides(color = "none")
plot_pd_conf
```

# 2nd order confidence

Computing the confidence

```{r}
cI_2o_plus <- cI.2o(XI_vector,zetaI.Pd,zetaI.Pd,roh_distribution.2o,1)
cI_2o_minus <- cI.2o (XI_vector,zetaI.Pd,zetaI.Pd,roh_distribution.2o,-1)
```


```{r}
df_cI_2o <- data.frame(yi = XI_vector,
                       cI_plus = cI_2o_plus,
                       cI_minus = cI_2o_minus)
df_cI_2o <- melt(df_cI_2o, id.vars = "yi")
```

Plotting

```{r}
plot_2o_conf <- ggplot(df_cI_2o, aes(x = yi, y = value, colour = variable)) + 
  geom_line(size = confidence_lsize) +
  coord_cartesian(xlim = c(-5,5), ylim = c(0,1)) +
  scale_x_continuous(breaks = fig1_xy_breaks_distributions,
                     name = bquote(Y[I]),
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(breaks = confidence_breaks,
                     name = "Confidence",
                     labels = scales::number_format(accuracy = 0.1))  +
  geom_vline(xintercept = 0,
             size = vertical_line_size) +
  geom_hline(yintercept = .5,
             linetype = "dashed",
             size = vertical_line_size) +
  scale_color_manual(values = palette_2ais,
                     name = "",
                     labels = c(bquote(a[I]*" = 1"),
                                bquote(a[I]*" = -1"))) +
  guides(colour = "none")
  
plot_2o_conf
```

```{r, fig.width=9.5, fig.height=9}
pls_fig1  <- pls_distributions / (plot_pd_conf | plot_2o_conf)
pls_fig1 
```



```{r,width=20, fig.height=11}
# ggsave(file = "output/MetaSearch_Fig1.svg", 
#        plot = pls_fig1,
#        width = 9.5, 
#        height = 9,
#        units = "in",
#        dpi = 300)
```










# Figure 2: Computations

## Parameters

We set the basic parameters

```{r}
sI <- 1.5
sF <- 1

# building the grid 
resolution <- 100
x <- seq(from = -5, to = 5, length.out = resolution) 
```

## Posterior based on $Z_I$ and value of not seeking

We first set this up

```{r}
df_ZIplot <- data.frame(XI = x)
df_ZIplot$posterior_positive <- sigmoid(2*x/sI^2)
df_ZIplot$posterior_negative <- 1-df_ZIplot$posterior_positive
# plot(df_ZIplot$posterior_negative)

# getting the maXImum
df_ZIplot$Q0 <- df_ZIplot$posterior_positive
df_ZIplot[which(df_ZIplot$Q0 < 0.5),]$Q0 <- 0.5 + abs(df_ZIplot[which(df_ZIplot$Q0 < 0.5),]$Q0 - .5)

# plot(df_ZIplot$v)
```


```{r}
pl_VandPosteriorAtI <- ggplot(data = df_ZIplot, aes(x = XI, y = Q0)) + 
  geom_line(size = lsize_intro + 2,
            colour = colour$Q0) +
  geom_line(aes(x = XI, y = posterior_negative), 
            size = lsize_intro,
            colour = colour$posterior_ZI,
            linetype = "dashed") +
  geom_line(aes(x = XI, y = posterior_positive),
            size = lsize_intro - .5,
            colour = colour$posterior_ZI) +
  scale_x_continuous(name=bquote(Z["I"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(name=bquote("P(d|"*Z[I]*") and "*Q["S"]*"(0)"), 
                     breaks=c(0,.5,1),
                     labels = scales::number_format(accuracy = 0.1)) +
  ggtitle(expression(bold("Posterior/Values from "*Z[I])))  
pl_VandPosteriorAtI
```


## Posterior for $Z_F$

```{r}
XI <- x
XF <- x

scaleFUN <- function(x) sprintf("%.2f", x)


zetaF2 <- 1/(1/(sI^2) + (1/sF^2))
ZF <- outer(XI/sI^2,XF/sF^2, FUN = "+")*zetaF2
ZFpost <- sigmoid(2*ZF/zetaF2)

# image(ZF)
# image(ZFpost)

df_ZFpost <- melt(ZFpost)
df_ZFpost$XI <- XI[df_ZFpost$Var1]
df_ZFpost$XF <- XF[df_ZFpost$Var2]

st_highcol <- "white"
st_lowcol <- "black"


pl_post <- ggplot(df_ZFpost, aes(x = XI, y = XF)) + 
  geom_tile(aes(fill=value)) +
  scale_fill_viridis_c(name = "Probability",
                      limits = c(0,1),
                      breaks = c(0,.5,1)) +
  coord_cartesian(xlim = c(-5,5), ylim = c(-5,5)) +
  scale_x_continuous(name=bquote(Z["I"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(name=bquote(X["F"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1)) +
  ggtitle(expression(bold("Posterior" ~ Z[F] * ": P(d=1|"*Z[F]*")"))) 
pl_post
```


## Value for ZF

```{r}
value_ZF <- 0.5 + abs(ZFpost -.5)
# image(df_ZFpost)
df_value_ZF <- melt(value_ZF)
df_value_ZF$XI <- XI[df_value_ZF$Var1]
df_value_ZF$XF <- XF[df_value_ZF$Var2]

pl_value_ZF <- ggplot(df_value_ZF, aes(x = XI, y = XF)) + 
  geom_tile(aes(fill=value)) +
  scale_fill_viridis_c(name = "Value",
                       limits = c(0.5,1),
                       breaks = c(.5,1),option = "magma") +
  coord_cartesian(xlim = c(-5,5), ylim = c(-5,5)) +
  scale_x_continuous(name=bquote(Z["I"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1)) +
  scale_y_continuous(name=bquote(X["F"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1))+
  ggtitle(expression(bold("Value of "*Z[F])))
pl_value_ZF
```


## Predicting $X_F$

```{r}
p_XF <- dnorm(x,mean = 1,sd = sF)
p_XF <- p_XF/sum(p_XF)
p_XFb <- dnorm(x,mean = -1,sd = sF)
p_XFb <- p_XFb/sum(p_XFb)

pXFXI <- outer(df_ZIplot$posterior_positive,p_XF) + outer(df_ZIplot$posterior_negative,p_XFb)
# image(pXFxI)

df_XFdis <- melt(pXFXI)
df_XFdis$xI <- XI[df_XFdis$Var1]
df_XFdis$XF <- XF[df_XFdis$Var2]


pl_XFXI <- ggplot(df_XFdis, aes(x = xI, y = XF)) + 
            geom_tile(aes(fill=value)) +
            scale_fill_viridis()+
            coord_cartesian(xlim = c(-5,5), ylim = c(-5,5)) +
            guides(fill=FALSE) +
            scale_x_continuous(name=bquote(Z["I"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1)) +
            scale_y_continuous(name=bquote(X["F"]), breaks=c(-5,0,5),
                               labels = scales::number_format(accuracy = 0.1)) + 
            ggtitle(expression(bold("p("*X[F]*"|"*Z[I]*")")))
pl_XFXI
```


## Q-Values

```{r}
Q1 <- rowSums(pXFXI*value_ZF) 

df_Qs <- data.frame(xI = x,
                  Q0 = df_ZIplot$Q0,
                  Q1_r0 = Q1,
                  Q1_r1 = Q1 - .1,
                  Q1_r2 = Q1 - .2, # adding different cost levels
                  Q1_r2 = Q1 - .3)

# getting this into a long dataframe
df_Qs_long <- melt(df_Qs, id.vars = c("xI", "Q0"),
                 value.name="Q1")

# adapting the costs so they plot right
df_Qs_long$Cost <- as.factor(rep(c(0, -.1,-.2,-.3), each = length(x)))
df_Qs_long$Cost <- factor(df_Qs_long$Cost, levels = rev(levels(df_Qs_long$Cost)))
```


```{r,fig.width=6, fig.height=5.5}
seekZone <- df_Qs$xI[which.min(df_Qs$diff)]


# colour_QS0 <-  "grey"

pl_Qs <- ggplot(data = df_Qs_long, aes(x = xI, y = Q1, colour = Cost)) + 
        geom_line(aes(x = xI, y = Q0), 
                            size = lsize_intro +1 , 
                            colour = colour$Q0) +        
          geom_line(size = lsize_intro + 1,) +
          scale_x_continuous(name=bquote(Z["I"]), breaks=c(-5,0,5),
                     labels = scales::number_format(accuracy = 0.1)) + 
          scale_y_continuous(name=bquote(Q[S]*"("*s[I]*")"), 
                             limits = c(.5,1),
                             breaks = seq(.5,1,.1)) +
          scale_color_manual(values = palette_4costs,
                             name = bquote(r[S])) +
          ggtitle("Q-Values") +
          guides(colour = "none") # +
          # annotate("text", x=1.8, y=.96, label= bquote(Q["S,0"]), 
          #      size = size_annotate,
          #      colour = colour$Q0) +
          # annotate("text", x= -3.5, y=.6, label= bquote(Q["S,1"]), 
          #    size = size_annotate,
          #    colour = "orange") 


pl_Qs
```


## Q-value difference

```{r}
df_Qs_long$diff <- abs(df_Qs_long$Q1 - df_Qs_long$Q0)
df_Qs_long$diffreal <- df_Qs_long$Q1 - df_Qs_long$Q0
df_Qs_long$cI <- sigmoid(2*df_Qs_long$xI/sI^2) 
df_Qs_long_half <- df_Qs_long[df_Qs_long$xI > 0,]
```


```{r}
pl_QdiffcI <- ggplot(data = df_Qs_long_half, aes(x = cI, y = diffreal, colour = Cost)) + 
  geom_hline(yintercept = 0, size = lsize_intro)+
  geom_line(size = lsize_intro + 1) +
  ylab(bquote("Q"[S]*"(1) -"*"Q"[S]*"(0)")) +
  xlab(bquote(c[I])) +
  scale_x_continuous(breaks = c(.5, .7, .9)) +
  scale_y_continuous(breaks = c(-.3,0,.3),
                     limits = c(-.3,.35)) +
  ggtitle("Q-Value difference") +
          scale_color_manual(values = palette_4costs,
                             name = bquote(r[S])) 
pl_QdiffcI
```


```{r}
softmax_temperature <- 20
df_Qs_long_half$decision <- sigmoid(softmax_temperature * df_Qs_long_half$diffreal)


pl_choice_prob <- ggplot(data = df_Qs_long_half, aes(x = cI, y = decision, colour = Cost)) + 
  geom_hline(yintercept = 0, size = lsize_intro)+
  geom_line(size = lsize_intro + 1) +
  ylab(bquote("Q"[S]*"(1) -"*"Q"[S]*"(0)")) +
  xlab(bquote(c[I])) +
  scale_x_continuous(breaks = c(.5, .7, .9)) +
  scale_color_manual(values = palette_4costs,
                     name = bquote(r[S])) 
  
pl_choice_prob

```


## Full figure

```{r, fig.width=20, fig.height=11}
margin <- .3
pl_fulls <- pl_VandPosteriorAtI +  pl_post + pl_value_ZF + pl_XFXI + pl_Qs + pl_QdiffcI +
  plot_layout(ncol = 3, guides = 'collect')&
  theme(plot.title = element_text(size = base_size*.85, face = "bold"),
        plot.tag = element_text(size = base_size, face = "bold", vjust = -.2),
        plot.margin = margin(margin,margin,margin,margin, unit = "cm"))
pl_fulls
```

## Saving

```{r,width=20, fig.height=11}
# ggsave(file = "output/MetaSearch_Components.pdf", 
#        plot = pl_fulls,
#        device = cairo_pdf, 
#        width = 20, 
#        height = 11,
#        units = "in",
#        dpi = 300)
```



